Data assimilation for the wave equation with discontinuous coefficients

### 2024-02-19 tex/main.tex
Update draft

\section{Introduction}
\noindent Let $\Omega \subset \mathbb{R}^d$ be a bounded domain such that there exists subdomains $\Omega_1, \Omega_2 \subseteq \Omega$ such that $\Omega = \overline{\Omega}_1 \cup \overline{\Omega}_2$ and $\Omega_1 \cap \Omega_2 = \emptyset$. We consider a scalar wave speed $c(x) = \mathbbm{1}_{\Omega_1} c_1(x) + \mathbbm{1}_{\Omega_2} c_2(x)$, $c_i \in C^\infty(\Omega_i)$, $i = 1,2$, which may be discontinuous across the interface $\Gamma = \Omega \setminus (\Omega_1 \cup \Omega_2)$, but constant in time.  
\noindent In this article, we consider the following problem: find $u \in Q \rightarrow \mathbb{R}$ such that 
\begin{subequations}
    \begin{alignat}{2}
        (\wop u, u) &= (0,0) \quad &&\text{ in } Q \times \Sigma, \\
        u &= u_{\omega} &&\text{ in } \omega_T,
    \end{alignat}    
\end{subequations}
where $\wop u := \partial_t^2 - \div(c(x)^2 \nabla u)$ is the wave operator and $u_{\omega}$ is the known data.

@@

\section{Discretization (fully discrete \& dG in time)} 
\noindent We introduce a similar scheme as considered in \cite{BP24}, but we incoporate the wave speed $c$. \textbf{spaces, etc..} \\
We introduce the bilinear form 
\begin{equation}
    A[\Uh,\Yh] := \sum_{n = 0}^{N -1} \left\{ (\dt \ul_2, \yl_1)_{Q^n} + a(\ul_1,\yl_1)_{Q^n} + (\dt \ul_1 - \ul_2,\yl_2)_{Q^n} - (c(x)^2 \nabla \ul_1 \cdot \mathbf{n}, \yl_1)_{\Sigma^n} \right\}
\end{equation} 
and the Lagrangian 
\begin{align*}
    \cL_h (\Uh, \Zh) := \frac{1}{2} \Vert \ul_1 - u_{\omega} \Vert^2_{\omega_T} + A[\Uh,\Zh] + \frac{1}{2} \gamma S_h(\Uh,\Uh) - \frac{1}{2} \gamma^\ast S_h^\ast(\Zh,\Zh) + \frac{\gamma}{2} \Sud(\Uh,\Uh).
\end{align*}
To define the stabilization terms $S_h$ and $S_h^\ast$, we introduce the following terms: 
\begin{align*}
    J(\Uh,\Wh) &:= \sum_{n = 0}^{N -1} \int_{I_n} \sum_{F \in \mathcal{F}_i} h (\jump{c(x)^2 \nabla \ul_1}, \jump{c(x)^2 \nabla \wl_1})_F \ \dT, \\
    I_0(\Uh,\Wh) &:= \sum_{n = 0}^{N -1} (\ul_2 - \dt \ul_1, \wl_2-\dt \wl_1)_{Q_n}, \\
    G(\Uh,\Wh) &:= \sum_{n = 0}^{N -1} \int_{I_n} \sum_{K \in \mathcal{T}_h} h^2 (\dt \ul_2 - \div (c(x)^2 \nabla \ul_1),\dt \wl_2 -\div( c(x)^2 \nabla \wl_1))_K \ \dT, \\
    R(\Uh,\Wh) &:= \sum_{n = 0}^{N -1} h^{-1} (\ul_1,\wl_1)_{\Sigma^n}. 
\end{align*}
Then, we define the primal stabilizer as 
\begin{equation}
    S_h(\Uh,\Wh) := J(\Uh,\Wh) + I_0(\Uh,\Wh) + G(\Uh,\Wh) + R(\Uh,\Wh), 
\end{equation}
and the dual stabilizer through 
\begin{equation}
    S_h^\ast(\Yh,\Zh) := \sum_{n = 0}^{N-1} \left\{ (\yl_1,\zl_1)_{Q^n} + a(\yl_1,\zl_1)_{Q^n} + (\yl_2,\zl_2)_{Q^n} + h^{-1} (\yl_1,\zl_1)_{\Sigma^n} \right\}.
\end{equation}
The stabilization term $\Sud$ imposes regularity on the discontinuities in time and is defined as 
\begin{equation}
    \Sud (\Uh,\Wh) := \underline{I}_1^{\uparrow \downarrow}(\Uh,\Wh) + \underline{I}_2^{\uparrow \downarrow}(\Uh,\Wh),
\end{equation}
where 
\begin{align*}
    \underline{I}_1^{\uparrow \downarrow}(\Uh,\Wh) &:= \sum_{n = 0}^{N-1} \left\{ \frac{1}{\Delta t} (\jump{\ul_1^n},\jump{\wl_1^n})_{\Omega} + \Delta t (c(x)^2 \jump{\nabla \ul_1^n},c(x)^2 \jump{\nabla \wl_1^n})_{\Omega}\right\}, \\
    \underline{I}_2^{\uparrow \downarrow}(\Uh,\Wh) &:= \sum_{n = 0}^{N-1} \frac{1}{\Delta t} (\jump{\ul_2^n},\jump{\wl_2^n})_{\Omega}.
\end{align*}

\noindent The first order optimality conditions then take the form: Find $(\Uh,\Zh) \in ...$ such that 
\begin{alignat*}{2}
    (\ul_1,\wl_1)_{\omega_T} + A[\Wh,\Zh] + \gamma S_h(\Uh,\Wh) + \Sud(\Uh,\Wh) &= (u_{\omega},\wl_1)_{\omega_T} \quad &&\forall \Wh \in ... \\
    A[\Uh,\Yh] - \gamma^{\ast} S_h^\ast(\Yh,\Zh) &= 0 \quad &&\forall \Yh \in ... 
\end{alignat*}
For convenience, we introduce
\begin{equation}
    \begin{aligned}
        B[(\Uh,\Zh),(\Wh,\Yh)] := &(\ul_1,\wl_1)_{\omega_T} + A[\Wh,\Zh]+ \gamma S_h(\Uh,\Wh) \\
        &+  \Sud(\Uh,\Wh) + A[\Uh,\Yh] - \gamma^{\ast} S_h^\ast(\Yh,\Zh),
    \end{aligned}
\end{equation}
such that the first order optimality conditions can be written as: Find $(\Uh,\Zh) \in ...$ such that
\begin{equation}
    B[(\Uh,\Zh),(\Wh,\Yh)] = (u_{\omega},\wl_1)_{\omega_T} \quad \forall (\Wh,\Yh) \in ...
\end{equation}

@@

\begin{lem}
    The expression $\tnorm{(\cdot,\cdot)}$ is a norm on ... 
\end{lem}

@@

\section{Numerical experiments}
\subsection{Example in one space dimension}
We consider the example from \cite{BDE22} with domain $\Omega = [0,1]$ that is partitioned into the subdomains $\Omega_1 = (0,0.5)$ and $\Omega_2 = (0.5,1.0)$ such that $\Omega = \overline{\Omega}_1 \cup \overline{\Omega}_2$. Then, we fix the wavespeed $c_2 := c \vert_{\Omega_2} = 1$ and consider different values for $c_1 := c \vert_{\Omega_1}$. With $u_0 (x) := \frac{1}{100} \exp(-(20(x-\frac{1}{5}))^2)$, the exact solution is given by 
\begin{equation}
    u(x,t) = \begin{cases}
      \sum_{k \ge 0} \left( \frac{c_2-c_1}{c_2+c_1}\right)^k \left( u_0 (k + x - c_1 t) 0- u_0(k-x-c_1 t)\right), x \in \Omega_1, \\
      \left( \frac{2c_1}{c_2+c_1}\right) \sum_{k \ge 0} \left( \frac{c_2 - c_1}{c_2 + c_1}\right)^k u_0 \left( \frac{c_1}{c_2} \left( x - \frac{1}{2}\right) +k + \frac{1}{2} - c_1 t \right), x \in \Omega_2. 
    \end{cases}
\end{equation}

>>>>

\section{Introduction}
\noindent Let $\Omega \subset \mathbb{R}^d$ be a bounded domain such that there exists subdomains $\Omega_1, \Omega_2 \subseteq \Omega$ such that $\Omega = \overline{\Omega}_1 \cup \overline{\Omega}_2$ and $\Omega_1 \cap \Omega_2 = \emptyset$. We consider a scalar wave speed $c(x) = \mathbbm{1}_{\Omega_1} c_1(x) + \mathbbm{1}_{\Omega_2} c_2(x)$, $c_i \in C^\infty(\Omega_i)$, $i = 1,2$, which may be discontinuous across the interface $\Gamma = \Omega \setminus (\Omega_1 \cup \Omega_2)$, but constant in time.  
\noindent In this article, we consider the following problem: find $u \in Q \rightarrow \mathbb{R}$ such that 
\begin{subequations}
    \begin{alignat}{2}
        (\wop u, u) &= (0,0) \quad &&\text{ in } Q \times \Sigma, \label{eq:waveEquation} \\ 
        u &= u_{\omega} &&\text{ in } \omega_T, \\ \label{eq:DataMatch}
    \end{alignat}    
\end{subequations}
where $\wop u := \partial_t^2 - \div(c(x)^2 \nabla u)$ is the wave operator and $u_{\omega}$ is the known data.

@@

\section{Discretization (fully discrete \& dG in time)} 
\noindent We introduce a similar scheme as considered in \cite{BP24}, but we incoporate the wave speed $c$. \textbf{spaces, etc..} \\
Let $\mathcal{T}_h$ be a quasi-uniform triangulation of $\Omega$ such that both, the data domain $\omega$ and the interface $\Gamma$ are fitted. We define the $H^1$-conforming finite element space 
\begin{equation}
    V_h^k := \{ v \in H^1(\Omega) : v \vert_{K} \in \mathcal{P}^k(K) \ \forall K \in \mathcal{T}_h \},
\end{equation}
where $\mathcal{P}^k(K)$ denotes the space of polynomials of degree at most $k \in \mathbb{N}$ on $K \in \mathcal{T}_h$. Furthermore, we partition the time axis into $N$ subinterals $I_n = (t_n,t_{n+1})$, $n = 0, \dots, N-1$, where $0 = t_0 \le t_1 \le \dots \le t_N = T$. We assume that the interavals are of equal length and denote $\Delta t = \vert t_{n+1} -t_n \vert$. Consequently, we can define a corresponding partition of $Q$ and $\Sigma$ into time-slabs 
\begin{equation}
    Q^n := I_n \times \Omega, \quad \Sigma^n := I_n \times \Sigma, n = 0, \dots, N-1, \qquad Q = \bigcup_{n = 0}^{N-1} Q^n, \quad \Sigma = \bigcup_{n = 0}^{N-1} \Sigma^n.
\end{equation}
Then, we define the discontinuous in time finite element spaces 
\begin{equation}
    \FullyDiscrSpace{k}{q} := \otimes_{n = 0}^{N-1} \mathcal{P}^q(I_n) \otimes V_h^k, \quad \ProdFullyDiscrSpace{k}{q} :=  \FullyDiscrSpace{k}{q} \times \FullyDiscrSpace{k}{q}, q \in \mathbb{N}_0, k \in \mathbb{N}. 
\end{equation}

We introduce the bilinear form 
\begin{equation}
    A[\Uh,\Yh] := \sum_{n = 0}^{N -1} \left\{ (\dt \ul_2, \yl_1)_{Q^n} + a(\ul_1,\yl_1)_{Q^n} + (\dt \ul_1 - \ul_2,\yl_2)_{Q^n} - (c(x)^2 \nabla \ul_1 \cdot \mathbf{n}, \yl_1)_{\Sigma^n} \right\}
\end{equation} 
and the Lagrangian 
\begin{align*}
    \cL_h (\Uh, \Zh) := \frac{1}{2} \Vert \ul_1 - u_{\omega} \Vert^2_{\omega_T} + A[\Uh,\Zh] + \frac{1}{2} \gamma S_h(\Uh,\Uh) - \frac{1}{2} \gamma^\ast S_h^\ast(\Zh,\Zh) + \frac{\gamma}{2} \Sud(\Uh,\Uh).
\end{align*}
To define the stabilization terms $S_h$ and $S_h^\ast$, we introduce the following terms: 
\begin{align*}
    J(\Uh,\Wh) &:= \sum_{n = 0}^{N -1} \int_{I_n} \sum_{F \in \mathcal{F}_i} h (\jump{c(x)^2 \nabla \ul_1}, \jump{c(x)^2 \nabla \wl_1})_F \ \dT, \\
    I_0(\Uh,\Wh) &:= \sum_{n = 0}^{N -1} (\ul_2 - \dt \ul_1, \wl_2-\dt \wl_1)_{Q_n}, \\
    G(\Uh,\Wh) &:= \sum_{n = 0}^{N -1} \int_{I_n} \sum_{K \in \mathcal{T}_h} h^2 (\dt \ul_2 - \div (c(x)^2 \nabla \ul_1),\dt \wl_2 -\div( c(x)^2 \nabla \wl_1))_K \ \dT, \\
    R(\Uh,\Wh) &:= \sum_{n = 0}^{N -1} h^{-1} (\ul_1,\wl_1)_{\Sigma^n}. 
\end{align*}
Then, we define the primal stabilizer as 
\begin{equation}
    S_h(\Uh,\Wh) := J(\Uh,\Wh) + I_0(\Uh,\Wh) + G(\Uh,\Wh) + R(\Uh,\Wh), 
\end{equation}
and the dual stabilizer through 
\begin{equation}
    S_h^\ast(\Yh,\Zh) := \sum_{n = 0}^{N-1} \left\{ (\yl_1,\zl_1)_{Q^n} + a(\yl_1,\zl_1)_{Q^n} + (\yl_2,\zl_2)_{Q^n} + h^{-1} (\yl_1,\zl_1)_{\Sigma^n} \right\}.
\end{equation}
The stabilization term $\Sud$ imposes regularity on the discontinuities in time and is defined as 
\begin{equation}
    \Sud (\Uh,\Wh) := \underline{I}_1^{\uparrow \downarrow}(\Uh,\Wh) + \underline{I}_2^{\uparrow \downarrow}(\Uh,\Wh),
\end{equation}
where 
\begin{align*}
    \underline{I}_1^{\uparrow \downarrow}(\Uh,\Wh) &:= \sum_{n = 0}^{N-1} \left\{ \frac{1}{\Delta t} (\jump{\ul_1^n},\jump{\wl_1^n})_{\Omega} + \Delta t (c(x)^2 \jump{\nabla \ul_1^n},c(x)^2 \jump{\nabla \wl_1^n})_{\Omega}\right\}, \\
    \underline{I}_2^{\uparrow \downarrow}(\Uh,\Wh) &:= \sum_{n = 0}^{N-1} \frac{1}{\Delta t} (\jump{\ul_2^n},\jump{\wl_2^n})_{\Omega}.
\end{align*}

\noindent The first order optimality conditions then take the form: Find $(\Uh,\Zh) \in ...$ such that 
\begin{alignat*}{2}
    (\ul_1,\wl_1)_{\omega_T} + A[\Wh,\Zh] + \gamma S_h(\Uh,\Wh) + \Sud(\Uh,\Wh) &= (u_{\omega},\wl_1)_{\omega_T} \quad &&\forall \Wh \in ... \\
    A[\Uh,\Yh] - \gamma^{\ast} S_h^\ast(\Yh,\Zh) &= 0 \quad &&\forall \Yh \in ... 
\end{alignat*}
For convenience, we introduce
\begin{equation}
    \begin{aligned}
        B[(\Uh,\Zh),(\Wh,\Yh)] := &(\ul_1,\wl_1)_{\omega_T} + A[\Wh,\Zh]+ \gamma S_h(\Uh,\Wh) \\
        &+  \Sud(\Uh,\Wh) + A[\Uh,\Yh] - \gamma^{\ast} S_h^\ast(\Yh,\Zh),
    \end{aligned}
\end{equation}
such that the first order optimality conditions can be written as: Find $(\Uh,\Zh) \in ...$ such that
\begin{equation}\label{eq:discreteProblem}
    B[(\Uh,\Zh),(\Wh,\Yh)] = (u_{\omega},\wl_1)_{\omega_T} \quad \forall (\Wh,\Yh) \in ...
\end{equation}

@@

\begin{lem}
    The expression $\tnorm{(\cdot,\cdot)}$ is a norm on $\ProdFullyDiscrSpace{k}{q} \times \ProdFullyDiscrSpace{k^\ast}{q^\ast}$.  
\end{lem}

@@

We recall the following interpolation results from \cite{BP24}:

\begin{lem}[Lem. 2.4 of \cite{BP24}]\label{lem:interpolationOperator}
    Assume that $\Delta t = Ch$ and set $(s,m) = (\min\{k,q\}, \max\{k,q\}+3)$.
    Then, there exists an interpolation operator $\Pi_h$ into $\FullyDiscrSpace{k}{q}$ such that for $n = 0, \dots, N-1$ the following estimates hold
    \begin{enumerate}
        \item $\sum_{n = 0}^{N-1} \{ h^{-1} \Vert u - \Pi_h u \Vert_{L^2(Q^n)} + \Vert \nabla(u - \Pi_h u) \Vert_{L^2(Q^n)} \} \le C \Vert u \Vert_{H^1(Q)}$. 
        \item $\sum_{n = 0}^{N-1} \{ h^{-1} \Vert u - \Pi_h u \Vert_{L^2(Q^n)} + \Vert u - \Pi_h u \Vert_{H^1(Q^n)} \} \le C h^{s} \Vert u \Vert_{H^{m-1}(Q)}$.
        \item $\left( \sum_{n = 0}^{N-1} \int_{I_n} \sum_{K \in \mathcal{T}_h} h^2 \Vert u - \Pi_h u \Vert^2_{H^2(K)} \ \dT \right)^{1/2} \le C h^{s} \Vert u \Vert_{H^{m}(Q)}$ for $u \in H^m(Q_n) \cap C^0(I_n,H^2(\Omega))$.
    \end{enumerate}
\end{lem}

\begin{lem}[Lem. 2.5 \& Lem. 4.2 of \cite{BP24}]
    In addition to the assumptions of Lem. \ref{lem:interpolationOperator}, let $u \in H^m(Q)$ solve \eqref{eq:waveEquation} and set $\mathbf{U} = (u,\partial_t u)$. Then, the following estimates hold true. 
    \begin{enumerate}
        \item For $u \in H^m(Q) \cap C^0([0,2],H^2(\Omega))$ we have that 
        \begin{equation}
            \vert \mathbf{\Pi}_h \mathbf{U} \vert_{S_h} = \vert \mathbf{\Pi}_h \mathbf{U} - \mathbf{U} \vert_{S_h} \le C h^{s} \Vert u \Vert_{H^m(Q)}.
        \end{equation}
        \item For $u \in H^m(Q)$ we have that
        \begin{equation}
            \vert \mathbf{\Pi}_h \mathbf{U} \vert_{\uparrow \downarrow} \le C h^{s} \Vert u \Vert_{H^{m-1}(Q)}.
        \end{equation}
        \item For $\Uh \in \ProdFullyDiscrSpace{k}{q}$ it holds that 
        \begin{equation}
            \Vert u - \ul_1 \Vert_{\Sigma} + \Vert u - \ul_1 \Vert_{\omega_T} \le C \left( h^{s+1/2} \Vert u \Vert_{H^m(Q)} + \tnorm{(\Uh - \mathbf{\Pi}_h \Uh,0)} \right).
        \end{equation}
        \item For $\mathbf{Y} = (y_1,y_2) \in [H^1(Q)]^2$, we have that
        \begin{equation}
            \Vert \mathbf{\Pi}^\ast_h \mathbf{Y} \Vert_{S_h^\ast} \le C \left( \Vert y_1 \Vert_{H^1(Q)} + \Vert y_2 \Vert_{H^2(Q)} \right). 
        \end{equation}
    \end{enumerate}
\end{lem}

\begin{thm}
    Let $u$ be a sufficient regular solution of \eqref{eq:waveEquation} and $(\Uh,\Zh) \in \ProdFullyDiscrSpace{k}{q} \times \ProdFullyDiscrSpace{k^\ast}{q^\ast}$ be the solution to \eqref{eq:discreteProblem}. Set $\mathbf{U} := (u,\partial_t u)$. Then, there exists a constant $C>0$ such that
    \begin{equation}
        \tnorm{(\Uh - \mathbf{\Pi}_h \mathbf{U},\Zh)} \le C h^s \Vert u \Vert_{H^m(Q)}.
    \end{equation}
\end{thm}

\section{Numerical experiments}
\noindent We choose the domain $\Omega = [0,1]$ which is partitioned into the subdomains $\Omega_1 = (0,0.5)$ and $\Omega_2 = (0.5,1.0)$ such that $\Omega = \overline{\Omega}_1 \cup \overline{\Omega}_2$. Then, we fix the wavespeed $c_2 := c \vert_{\Omega_2} = 1$ and consider different values for $c_1 := c \vert_{\Omega_1}$.

\subsection{Example in one space dimension}
As a first example, we consider the exact solution
\begin{equation}\label{eq:1D:exact:simple}
    u(x,t) := \begin{cases}
        \cos(w_1 c_1 t) \cos(w_1(x-0.5)), & x \in \Omega_1, \\
        \cos(w_2 c_2 t) \cos(w_2(x-0.5)), & x \in \Omega_2,
    \end{cases}
\end{equation}
where we set $w_1 = 3 \pi$ and $w_2 = w_1 c_1 / c_2$. We compute until $T = 1.0$ to ensure that the GCC is fulfilled.

\begin{figure}[!htbp]
    \begin{center}
        \begin{tikzpicture}[scale=0.72]
            \begin{groupplot}[%
                group style={%
                group size=2 by 1,
                horizontal sep=1.5cm,
                vertical sep=2cm,
                },
            ymajorgrids=true,
            grid style=dashed,
            %ymin = 1e-3, ymax = 0.5e1,
            ]    
                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u$ vs. $u_h$ ($k = 3$)}, %cycle list name=paulcolors, 
                legend pos=north west, %yticklabels={,,},
                ]
                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
                \addplot+[discard if not={L}{1},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_approx_plot_data_WPFalse_contrast2.5_k3.csv};
                \addplot+[discard if not={L}{2},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_approx_plot_data_WPFalse_contrast2.5_k3.csv};
                \addplot+[discard if not={L}{3},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_approx_plot_data_WPFalse_contrast2.5_k3.csv};

                \draw[dashed,gray,very thick] (0.5,-2) -- (0.5,2);
                \node [draw=none] at (axis description cs:0.45,0.23) {\color{gray} $\Gamma$};

                \legend{$L=1$, $L=2$, $L=3$}
                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$\Vert \partial_t (u - u_h) \Vert_{L^2(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors, 
                legend pos=south west, %yticklabels={,,},
                ]
                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
                \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k2_WPFalse.csv};
                \addplot+[discard if not={order}{2}, discard if not={contrast}{2.5},line width=1.1pt] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k2_WPFalse.csv};
                \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
                \addplot+[discard if not={order}{3}, discard if not={contrast}{2.5},line width=1.1pt] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k3_WPFalse.csv};
                \addplot[gray, dashed, domain=1:4] {15*(1/2^(2))^(x-0.9)};
                \addplot[gray, dashed, domain=1:4] {7.5*(1/2^(3))^(x-0.9)};
                \node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
                \node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
                \legend{$k=2$,best, $k = 3$, best}
            \end{groupplot}
        \end{tikzpicture}
    \end{center}
    \caption{Approximation of \eqref{eq:1D:exact:simple} with $c_1 = 2.5$}
    \label{fig:jumpCoefs:contrast:2.5}
  \end{figure}

  \begin{figure}[!htbp]
    \begin{center}
        \begin{tikzpicture}[scale=0.72]
            \begin{groupplot}[%
                group style={%
                group size=2 by 1,
                horizontal sep=1.5cm,
                vertical sep=2cm,
                },
            ymajorgrids=true,
            grid style=dashed,
            %ymin = 1e-3, ymax = 0.5e1,
            ]    
                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=linear, xlabel={}, ylabel={}, title={$u$ vs. $u_h$ ($k = 3$)}, %cycle list name=paulcolors, 
                legend pos=north west, %yticklabels={,,},
                ]
                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
                \addplot+[discard if not={L}{1},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_approx_plot_data_WPFalse_contrast5.5_k3.csv};
                \addplot+[discard if not={L}{2},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_approx_plot_data_WPFalse_contrast5.5_k3.csv};
                \addplot+[discard if not={L}{3},line width=1.1pt,mark=None] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_approx_plot_data_WPFalse_contrast5.5_k3.csv};

                \draw[dashed,gray,very thick] (0.5,-2) -- (0.5,2);
                \node [draw=none] at (axis description cs:0.45,0.23) {\color{gray} $\Gamma$};

                \legend{$L=1$, $L=2$, $L=3$}
                \nextgroupplot[width=9cm,height=7cm,domain=0:1,xmode=linear,ymode=log, xlabel={}, ylabel={}, title={$\Vert \partial_t (u - u_h) \Vert_{L^2(0,T;L^2(\Omega))}$}, %cycle list name=paulcolors, 
                legend pos=south west, %yticklabels={,,},
                ]
                %\addplot+[discard if not={contrast}{1.0},line width=2.5pt,mark=None,color=black] table [x=x, y=y, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/exact_plot_data.csv};
                \addplot+[discard if not={order}{2}, discard if not={contrast}{5.5},line width=1.1pt] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k2_WPFalse_contrast5.5.csv};
                \addplot+[discard if not={order}{2}, discard if not={contrast}{5.5},line width=1.1pt] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k2_WPFalse_contrast5.5.csv};
                \addplot+[discard if not={order}{3}, discard if not={contrast}{5.5},line width=1.1pt] table [x=L, y=L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k3_WPFalse_contrast5.5.csv};
                \addplot+[discard if not={order}{3}, discard if not={contrast}{5.5},line width=1.1pt] table [x=L, y=bestapprox-L2-L2-error-u_t, col sep=comma] {../../wave_data_assimilation/data/jumpCoefs/newexact_1D_jumpingCoefs_k3_WPFalse_contrast5.5.csv};
                \addplot[gray, dashed, domain=1:4] {15*(1/2^(2))^(x-0.9)};
                \addplot[gray, dashed, domain=1:4] {7.5*(1/2^(3))^(x-0.9)};
                \node [draw=none] at (axis description cs:0.80,0.40) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{2})$};
                \node [draw=none] at (axis description cs:0.65,0.2) {\color{gray}\footnotesize $\!\!\mathcal{O}(h^{3})$};
                \legend{$k=2$,best, $k = 3$, best}
            \end{groupplot}
        \end{tikzpicture}
    \end{center}
    \caption{Approximation of \eqref{eq:1D:exact:simple} with $c_1 = 5.5$}
    \label{fig:jumpCoefs:contrast:5.5}
  \end{figure}

\subsection{2nd one dimensional example}
We consider the example from \cite{BDE22}. With $u_0 (x) := \frac{1}{100} \exp(-(20(x-\frac{1}{5}))^2)$, the exact solution is given by 
\begin{equation}
    u(x,t) = \begin{cases}
      \sum_{k \ge 0} \left( \frac{c_2-c_1}{c_2+c_1}\right)^k \left( u_0 (k + x - c_1 t) 0- u_0(k-x-c_1 t)\right), x \in \Omega_1, \\
      \left( \frac{2c_1}{c_2+c_1}\right) \sum_{k \ge 0} \left( \frac{c_2 - c_1}{c_2 + c_1}\right)^k u_0 \left( \frac{c_1}{c_2} \left( x - \frac{1}{2}\right) +k + \frac{1}{2} - c_1 t \right), x \in \Omega_2. 
    \end{cases}
\end{equation}
